---
title: "Player Tracking"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

<style>.dataTables_scrollBody {
    max-height: 100% !important;
}
</style>

```{r setup, include=FALSE}

##options(repos = list(CRAN="http://cran.rstudio.com/"))

library(flexdashboard)
library(tidyverse)
library(readxl)
library(here)
library(knitr)
library(lubridate)
library(dplyr)
library(reshape2)
library(plotly)
library(crosstalk)
library(broom)
library(DT)
library(kableExtra)
library(ggthemes)

##Game 1 tracking data
Game1_Tracking_AwayTeam <- read_csv(here("Data","Sample_Game_1_RawTrackingData_Away_Team.csv"),skip = 3, col_names = F)

Game1_ColNames <- read_csv(here("Data","Sample_Game_1_RawTrackingData_Away_Team.csv"), n_max = 2)

colnames(Game1_Tracking_AwayTeam) <- c(as.character(Game1_ColNames[2,]))
colnames(Game1_Tracking_AwayTeam)[32] <- c("Ball_X")
colnames(Game1_Tracking_AwayTeam)[33] <- c("Ball_Y")
colnames(Game1_Tracking_AwayTeam)[3] <- c("Time")

num_1 <- na.omit(as.numeric(Game1_ColNames[1,])) 
name_1 <- as.character(Game1_ColNames[2,-c(1:3)])
name_1 <- name_1[name_1 != "NA"] 
name_1 <- str_replace_all(name_1, " ", "")

name_X <- paste0(name_1, "_X") 
name_Y <- paste0(name_1, "_Y")

X.inds <- seq(4, ncol(Game1_Tracking_AwayTeam)-2, by = 2) 
Y.inds <- seq(5, ncol(Game1_Tracking_AwayTeam)-2, by = 2) 
names(Game1_Tracking_AwayTeam)[X.inds] <- name_X 
names(Game1_Tracking_AwayTeam)[Y.inds] <- name_Y 


##Game 1 events data
Game1_Events <- read_csv(here("Data","Sample_Game_1_RawEventsData.csv"))


##Game 2 tracking data
Game2_Tracking_AwayTeam <- read_csv(here("Data","Sample_Game_2_RawTrackingData_Away_Team.csv"),skip = 3, col_names = F)

Game2_ColNames <- read_csv(here("Data","Sample_Game_2_RawTrackingData_Away_Team.csv"), n_max = 2)

colnames(Game2_Tracking_AwayTeam) <- c(as.character(Game2_ColNames[2,]))
colnames(Game2_Tracking_AwayTeam)[28] <- c("Ball_X")
colnames(Game2_Tracking_AwayTeam)[29] <- c("Ball_Y")
colnames(Game2_Tracking_AwayTeam)[3] <- c("Time")

num_2 <- na.omit(as.numeric(Game2_ColNames[1,])) 
name_2 <- as.character(Game2_ColNames[2,-c(1:3)])
name_2 <- name_2[name_2 != "NA"] 
name_2 <- str_replace_all(name_2, " ", "")

name2_X <- paste0(name_2, "_X") 
name2_Y <- paste0(name_2, "_Y")

X.inds2 <- seq(4, ncol(Game2_Tracking_AwayTeam)-2, by = 2) 
Y.inds2 <- seq(5, ncol(Game2_Tracking_AwayTeam)-2, by = 2) 
names(Game2_Tracking_AwayTeam)[X.inds2] <- name2_X 
names(Game2_Tracking_AwayTeam)[Y.inds2] <- name2_Y 


##Game 2 events data
Game2_Events <- read_csv(here("Data","Sample_Game_2_RawEventsData.csv"))

##Assessement data
Assessment <- read_csv(here("Data","Assessement_Data.csv"))

toDelete <- seq(1, nrow(Assessment), 2)
Assessment <- Assessment[-toDelete ,]


##Removing duplicate from dataframe that includes max running speed
##Does not work as it appears to be assessing only first or last values 
##and not the whole observation
##
##test <- Assessment[duplicated(Assessment[,4:6]),]

NoMaxRunning <- subset(Assessment, Assessment$assessment != "Max Running Speed")

duplicates <- NoMaxRunning[duplicated(NoMaxRunning[,4:6]),]

NoDuplicates <- NoMaxRunning[!duplicated(NoMaxRunning[,4:6]),]

duplicateAverages <- duplicates %>% group_by(athletes,date,metric) %>% mutate(value=round(mean(value),4)) %>% slice(1)

FinalAssessment <- rbind(NoDuplicates,duplicateAverages)

FinalAssessment$date <- as.Date(FinalAssessment$date, format = "%m/%d/%y")


MaxRunningSpeed <- subset(Assessment, Assessment$assessment == "Max Running Speed")

SprintSpeed30Y <- subset(MaxRunningSpeed, MaxRunningSpeed$metric == "0-30y")

SprintSpeed30Y$date <- as.Date(SprintSpeed30Y$date, format = "%m/%d/%y")

SprintDuplicates <- SprintSpeed30Y[duplicated(SprintSpeed30Y[,4:6]),]

SprintAverages <- SprintDuplicates %>% group_by(athletes,date,metric) %>% mutate(value=round(mean(value),4)) %>% slice(1)

FinalAssessment <- rbind(FinalAssessment,SprintAverages)


FinalAssessment <- FinalAssessment[order(FinalAssessment$athletes, FinalAssessment$date),]


##Testing making each metric a header and filling values as observations
sepTest <- FinalAssessment[ , c(1,4,6:7)]

flipTest <- dcast(sepTest,athletes + date + value~metric)


##Testing grabbing just the most recent value for each metric using ##athlete 1
athlete1Test <- subset(Assessment, Assessment$athletes == "athlete 1")

mostRecent <- athlete1Test %>% group_by(metric) %>% summarise(Last_value = last(value))

##Pulling the most recent value for each metric for all athletes
allMostRecent <- FinalAssessment %>% group_by(athletes,metric) %>% summarise(Last_value = last(value))

sum(is.na(allMostRecent))

#calculate quantiles by metric
q = c(.30, .60, .90)

quantiles <- allMostRecent %>%
  group_by(metric) %>%
  summarize(quant30 = quantile(Last_value, probs = q[1]), 
            quant60 = quantile(Last_value, probs = q[2]),
            quant90 = quantile(Last_value, probs = q[3]))


quantileMerge <- merge(allMostRecent,quantiles, by="metric")

quantileMerge <- quantileMerge %>% mutate(level = with(quantileMerge, ifelse(Last_value <= quant30, "Poor",
          ifelse(Last_value > quant30 & Last_value <= quant60, "Average",
                 ifelse(Last_value > quant60 & Last_value  <= quant90, "Good", "Excellent")))))
                 








```

Metric Definitions and Evaluation
==============================================================

Column 
-------------------------------------

### Definitions

a)

- Concentric Impulse: Force output at takeoff of jump.

- Concentric Impulse - 100ms: Force applied in the first 100ms of jump motion.

- Concentric Mean Power / Body Weight: Mean force applied during the takeoff phase.

- Eccentric Mean Power / Body Weight: Mean force applied during loading phase. 

- RSI - Modified: Ratio of flight time and time in contact with the ground or 
  how high and how fast.

- Vertical Velocity @ Take off: How fast an individual leaves the ground 

Column 
-------------------------------------

### Thougths on Metrics 

b)

- I believe this is a good combination of metrics not just for the sport presented
  but for all sports. 

- There is a good combination of strength, power, speed, and endurance to get a            complete picture of an individuals overall athleticism and readiness to perform. 

- With my background knowledge of the sport in question as well as various fitness
  metrics, no additional measurements come to mind to add to the list provided. 
  
- As mentioned before, I believe this is a good combination, or at the least a very
  good starting point for being able to gauge an individuals athleticism. 

Most Recent Assessments 
==============================================================

Column {data-width=1000, data-height=1000}
--------------------------------------------------------------


```{r, plotly-crosstalk, out.height="100%"}



shared_Quantiles <- SharedData$new(quantileMerge, group = "shared_obj")

# send the group to the filtering selection box
filter_select(id = "id-selector", label = "Athlete",                                              sharedData = shared_Quantiles, group = ~ athletes)
filter_select(id = "id-selector", label = "Level", 
            sharedData = shared_Quantiles, group = ~ level)
filter_checkbox(id = "id-selector", label = "Metric", 
             sharedData = shared_Quantiles, group = ~ metric, columns = 7)


# datatable(shared_Quantiles, fillContainer = TRUE)



# pal <- c("red", "yellow", "green", "blue")
# pal <- setNames(pal, c("Poor", "Average", "Good", "Excellent"))
##fill = list(color=list(pal))

# shared_quantileMerge <- SharedData$new(quantileMerge)
# 
# 
# 
# fig2 <- shared_quantileMerge %>% plot_ly(
#   type = 'table',
#   columnwidth = c(500) ,
#   header = list(
#     values = c("Record",names(quantileMerge)),
#   align = c('left', rep('center', ncol(quantileMerge))),
#   line = list(width = 1, color = 'black'),
#   fill = list(color = 'rgb(202, 210, 222)'),
#   font = list(family = "Arial", size = 14, color = "black")
#   ),
#   cells = list(
#     values = rbind(
#       rownames(quantileMerge), 
#       t(as.matrix(unname(quantileMerge)))
#     ),
#     align = c('left', rep('center', ncol(quantileMerge))),
#     line = list(color = "black", width = 1),
#     fill = list(color = c('white')),
#     font = list(family = "Arial", size = 12, color = c("black"))
#   ))
# 
# 
# filter_checkbox(id = "metric", label = "Metric",
#                 sharedData = shared_quantileMerge, group = ~metric)
# filter_select(id = "athletes", label = "Athlete",
#              sharedData = shared_quantileMerge, group = ~athletes)
#       
# 
# fig2


# bscols(
#        list(
#             filter_checkbox(id = "metric", label = "Metric",
#                     sharedData = shared_quantileMerge, group = ~metric),
#             filter_select(id = "athletes", label = "Athlete",
#                     sharedData = shared_quantileMerge, group = ~athletes)
#       ),
# 
# 
# fig2)




# fill = list(color = ~ quantileMerge$level,
#     colors = c("red", "yellow", "green", "blue"))

# fill = dict(color='rgb(245, 245, 245)',
#                                             'rgb(242, 63, 63)' if val = "Poor" else 'rgb(237, 221, 38)' if val = "Average"  else 'rgb(88, 237, 38)' if val = "Good" else 'rgb(38, 230, 237)' for val in vals ),

# 
# fill = list(color = c('rgb(235, 193, 238)', 'rgb(235, 193, 238)','rgb(235, 193, 238)','rgb(235, 193, 238)','rgb(235, 193, 238)','rgb(235, 193, 238)','rgb(235, 193, 238)', 'rgba(228, 222, 249, 0.65)'))

```


```{r}

datatable(shared_Quantiles, fillContainer = TRUE)

```


Historical Assessments
==============================================================

Column {data-width=1000, data-height=1000}
--------------------------------------------------------------


```{r}

shared_Assessments <- SharedData$new(FinalAssessment, group = "shared_obj")

# send the group to the filtering selection box
filter_select(id = "id-selector", label = "Athlete",                                              sharedData = shared_Assessments, group = ~ athletes)
filter_select(id = "id-selector", label = "Position", 
            sharedData = shared_Assessments, group = ~ position)
filter_select(id = "id-selector", label = "Metric", 
             sharedData = shared_Assessments, group = ~ metric)


datatable(shared_Assessments)
```


Change Over Time
==============================================================

Column {data-width=1000, data-height=1000}
--------------------------------------------------------------


```{r}


shared_data <- SharedData$new(FinalAssessment, group = "shared_obj")


p <- shared_data %>% 
  plot_ly(x = ~date, y = ~value,
              hoverinfo = "text",
              type = "scatter",
              mode ="lines",
              color = "metric",
              text = ~paste("Athlete:", athletes,
                            "<br>date:", date,
                            "<br>metric:", metric,
                            "<br>value:", value)) %>% 
  group_by(metric) %>% 
  add_markers(size = 3) %>%
  layout(xaxis = list(title = "Date"),
         yaxis = list(title = "Metric Value"),
         legend = list(font = list(size = 16)))



filter_checkbox(id = "metric", label = "Metric",
                sharedData = shared_data, group = ~metric, columns = 7)
filter_select(id = "athlete", label = "Athlete",
                sharedData = shared_data, group = ~athletes)
           
p





# p <- ggplot(athlete1Flip, aes(x=date, y=`Body Fat %`)) +
#   geom_point() +
#   geom_line(data=athlete1Flip[!is.na(athlete1Flip$`Body Fat %`),],aes(x=date, y= `Body Fat %`), color="black")
# 
#         
# p


# for(i in 1:nlevels(athlete1Test$metric)) {
#   
#   p <- ggplot(athlete1Test[athlete1Test$metric == levels(athlete1Test$metric)[i]], aes(x=date, y=metric)) +
#   geom_point() +
#   geom_line()
# 
# p
# 
# }


# athlete1Flip <- subset(flipTest, flipTest$athletes == "athlete 1")
# 
# p <- ggplot(athlete1Flip, aes(x=date, y=`Body Fat %`)) +
#   geom_point() +
#   geom_line(data=athlete1Flip[!is.na(athlete1Flip$`Body Fat %`),],aes(x=date, y= `Body Fat %`), color="black")
# 
#         
# p





```


Game 1 Match Analysis
==============================================================


Column
--------------------------------------------------------------

### Distance Traveled 

```{r}

Game1_Tracking_AwayTeam[is.na(Game1_Tracking_AwayTeam)] <- 0

rows <- nrow(Game1_Tracking_AwayTeam)
  
# difference in rows of entire dataframe
Game1rowDiffernces <- abs(Game1_Tracking_AwayTeam[-1,] - Game1_Tracking_AwayTeam[-rows,])

Game1_Tracking_AwayTeam <- Game1_Tracking_AwayTeam %>% mutate(Game1_Tracking_AwayTeam,       Player15_dist_travelled = sqrt((Player15_X - lag(Player15_X))^2 + (Player15_Y - lag(Player15_Y))^2),
      Player16_dist_travelled = sqrt((Player16_X - lag(Player16_X))^2 + (Player16_Y - lag(Player16_Y))^2),
      Player17_dist_travelled = sqrt((Player17_X - lag(Player17_X))^2 + (Player17_Y - lag(Player17_Y))^2) ,
      Player18_dist_travelled = sqrt((Player18_X - lag(Player18_X))^2 + (Player18_Y - lag(Player18_Y))^2) ,
      Player19_dist_travelled = sqrt((Player19_X - lag(Player19_X))^2 + (Player19_Y - lag(Player19_Y))^2) ,
      Player20_dist_travelled = sqrt((Player20_X - lag(Player20_X))^2 + (Player20_Y - lag(Player20_Y))^2) ,
      Player21_dist_travelled = sqrt((Player21_X - lag(Player21_X))^2 + (Player21_Y - lag(Player21_Y))^2) ,
      Player22_dist_travelled = sqrt((Player22_X - lag(Player22_X))^2 + (Player22_Y - lag(Player22_Y))^2) ,
      Player23_dist_travelled = sqrt((Player23_X - lag(Player23_X))^2 + (Player23_Y - lag(Player23_Y))^2) ,
      Player24_dist_travelled = sqrt((Player24_X - lag(Player24_X))^2 + (Player24_Y - lag(Player24_Y))^2) ,
      Player25_dist_travelled = sqrt((Player25_X - lag(Player25_X))^2 + (Player25_Y - lag(Player25_Y))^2) ,
      Player26_dist_travelled = sqrt((Player26_X - lag(Player26_X))^2 + (Player26_Y - lag(Player26_Y))^2) ,
      Player27_dist_travelled = sqrt((Player27_X - lag(Player27_X))^2 + (Player27_Y - lag(Player27_Y))^2) ,
      Player28_dist_travelled = sqrt((Player28_X - lag(Player28_X))^2 + (Player28_Y - lag(Player28_Y))^2)  )


game1TotalDistance <- data.frame(colSums(Game1_Tracking_AwayTeam[,-c(1:33)], na.rm = TRUE))

game1TotalDistance['Player'] <- as.character(c(25,15:24,26:28))

colnames(game1TotalDistance)[1] <- "Total_Distance"


p <-ggplot(data=game1TotalDistance, aes(x=Player, y=Total_Distance)) +
  geom_bar(stat="identity", color="black", fill="lightblue")+
  labs(title="Total Distance Traveled during Game 1", x="Player", y = "Distance")

p



```

### Average Speed 

```{r}

Game1_Tracking_AwayTeam <- Game1_Tracking_AwayTeam %>% mutate(Game1_Tracking_AwayTeam,       Player15_speed = (Player15_dist_travelled/Time),
      Player16_speed = (Player16_dist_travelled/Time),
      Player17_speed = (Player17_dist_travelled/Time),
      Player18_speed = (Player18_dist_travelled/Time),
      Player19_speed = (Player19_dist_travelled/Time),
      Player20_speed = (Player20_dist_travelled/Time),
      Player21_speed = (Player21_dist_travelled/Time),
      Player22_speed = (Player22_dist_travelled/Time),
      Player23_speed = (Player23_dist_travelled/Time),
      Player24_speed = (Player24_dist_travelled/Time),
      Player25_speed = (Player25_dist_travelled/Time),
      Player26_speed = (Player26_dist_travelled/Time),
      Player27_speed = (Player27_dist_travelled/Time),
      Player28_speed = (Player28_dist_travelled/Time))

game1Speeds <- Game1_Tracking_AwayTeam[c(48:61)]

game1Speeds[game1Speeds==0] <- NA
                                                    
game1AverageSpeed <- data.frame(colMeans(game1Speeds, na.rm = TRUE))

game1AverageSpeed['Player'] <- as.character(c(15:28))

colnames(game1AverageSpeed)[1] <- "Avg_Speed"


p <-ggplot(data=game1AverageSpeed, aes(x=Player, y=Avg_Speed)) +
  geom_bar(stat="identity", color="black", fill="lightblue")+
  labs(title="Average Speed during Game 1", x="Player", y = "Average Speed")

p

```

Column
--------------------------------------------------------------

### Shot Attemps by Team

```{r}

Game1Shots <- subset(Game1_Events, Game1_Events$Type == "SHOT")

ggplot(data=Game1Shots, aes(fill=Type, x=Team)) + 
  geom_bar(position="stack", stat = "count", color="black", fill="lightblue") +
 labs(title = "Shot Attempts by Team", x = "Team", y = "Count") 

```

### Interceptions by Team

```{r}

Game1Interceptions <- subset(Game1_Events, Game1_Events$Subtype == "INTERCEPTION")

ggplot(data=Game1Interceptions, aes(fill=Subtype, x=Team)) + 
  geom_bar(position="stack", stat = "count", color="black", fill="lightblue") +
 labs(title = "Interceptions by Team", x = "Team", y = "Count") 

```


Game 2 Match Analysis
==============================================================

Column
--------------------------------------------------------------

### Distance Traveled 

```{r}

Game2_Tracking_AwayTeam[is.na(Game2_Tracking_AwayTeam)] <- 0

rows <- nrow(Game2_Tracking_AwayTeam)
  
# difference in rows of entire dataframe
Game2rowDiffernces <- abs(Game2_Tracking_AwayTeam[-1,] - Game2_Tracking_AwayTeam[-rows,])

Game2_Tracking_AwayTeam <- Game2_Tracking_AwayTeam %>% mutate(Game2_Tracking_AwayTeam,       Player15_dist_travelled = sqrt((Player15_X - lag(Player15_X))^2 + (Player15_Y - lag(Player15_Y))^2),
      Player16_dist_travelled = sqrt((Player16_X - lag(Player16_X))^2 + (Player16_Y - lag(Player16_Y))^2),
      Player17_dist_travelled = sqrt((Player17_X - lag(Player17_X))^2 + (Player17_Y - lag(Player17_Y))^2) ,
      Player18_dist_travelled = sqrt((Player18_X - lag(Player18_X))^2 + (Player18_Y - lag(Player18_Y))^2) ,
      Player19_dist_travelled = sqrt((Player19_X - lag(Player19_X))^2 + (Player19_Y - lag(Player19_Y))^2) ,
      Player20_dist_travelled = sqrt((Player20_X - lag(Player20_X))^2 + (Player20_Y - lag(Player20_Y))^2) ,
      Player21_dist_travelled = sqrt((Player21_X - lag(Player21_X))^2 + (Player21_Y - lag(Player21_Y))^2) ,
      Player22_dist_travelled = sqrt((Player22_X - lag(Player22_X))^2 + (Player22_Y - lag(Player22_Y))^2) ,
      Player23_dist_travelled = sqrt((Player23_X - lag(Player23_X))^2 + (Player23_Y - lag(Player23_Y))^2) ,
      Player24_dist_travelled = sqrt((Player24_X - lag(Player24_X))^2 + (Player24_Y - lag(Player24_Y))^2) ,
      Player25_dist_travelled = sqrt((Player25_X - lag(Player25_X))^2 + (Player25_Y - lag(Player25_Y))^2) ,
      Player26_dist_travelled = sqrt((Player26_X - lag(Player26_X))^2 + (Player26_Y - lag(Player26_Y))^2) )


game2TotalDistance <- data.frame(colSums(Game2_Tracking_AwayTeam[,-c(1:29)], na.rm = TRUE))

game2TotalDistance['Player'] <- as.character(c(25,15:24,26))

colnames(game2TotalDistance)[1] <- "Total_Distance"


p <-ggplot(data=game2TotalDistance, aes(x=Player, y=Total_Distance)) +
  geom_bar(stat="identity", color="black", fill="lightblue")+
  labs(title="Total Distance Traveled during Game 2", x="Player", y = "Distance")

p




```

### Average Speed

```{r}
Game2_Tracking_AwayTeam <- Game2_Tracking_AwayTeam %>% mutate(Game2_Tracking_AwayTeam,       Player15_speed = (Player15_dist_travelled/Time),
      Player16_speed = (Player16_dist_travelled/Time),
      Player17_speed = (Player17_dist_travelled/Time),
      Player18_speed = (Player18_dist_travelled/Time),
      Player19_speed = (Player19_dist_travelled/Time),
      Player20_speed = (Player20_dist_travelled/Time),
      Player21_speed = (Player21_dist_travelled/Time),
      Player22_speed = (Player22_dist_travelled/Time),
      Player23_speed = (Player23_dist_travelled/Time),
      Player24_speed = (Player24_dist_travelled/Time),
      Player25_speed = (Player25_dist_travelled/Time),
      Player26_speed = (Player26_dist_travelled/Time))

game2Speeds <- Game2_Tracking_AwayTeam[c(42:53)]

game2Speeds[game2Speeds==0] <- NA
                                                    
game2AverageSpeed <- data.frame(colMeans(game2Speeds, na.rm = TRUE))

game2AverageSpeed['Player'] <- as.character(c(15:26))

colnames(game2AverageSpeed)[1] <- "Avg_Speed"


p <-ggplot(data=game2AverageSpeed, aes(x=Player, y=Avg_Speed)) +
  geom_bar(stat="identity", color="black", fill="lightblue")+
  labs(title="Average Speed during Game 2", x="Player", y = "Average Speed")

p

```

Column
--------------------------------------------------------------

### Shot Attemps by Team

```{r}
Game2Shots <- subset(Game2_Events, Game2_Events$Type == "SHOT")

ggplot(data=Game2Shots, aes(fill=Type, x=Team)) + 
  geom_bar(position="stack", stat = "count", color="black", fill="lightblue") +
 labs(title = "Shot Attempts by Team", x = "Team", y = "Count") 

```


### Interceptions by Team

```{r}

Game2Interceptions <- subset(Game2_Events, Game2_Events$Subtype == "INTERCEPTION")

ggplot(data=Game2Interceptions, aes(fill=Subtype, x=Team)) + 
  geom_bar(position="stack", stat = "count", color="black", fill="lightblue") +
 labs(title = "Interceptions by Team", x = "Team", y = "Count") 

```
